Using pressure-driven flow systems to evaluate laser speckle contrast imaging

### 2022-08-04 article.tex
Updated Adam's bio
Add Pawan to authors. Add bios for Chris and Pawan.

\author[a]{Colin T. Sullender}
\author[a]{Adam Santorelli}
\author[a]{Christopher Smith}
\author[a]{Lisa M. Richards}
\author[a,*]{Andrew K. Dunn}
\affil[a]{Department of Biomedical Engineering, The University of Texas at Austin, Austin, TX, 78712, USA}

@@

\subsection*{Author Contributions}
C.T.S. and L.M.R. constructed the imaging system, conceived the experiments, and acquired the data. C.T.S., A.S., and L.M.R. analyzed the results and wrote the manuscript. A.K.D. supervised the project. All authors contributed to manuscript revisions.

@@

\vspace{2ex}\noindent\textbf{Adam Santorelli} is a research associate at the University of Texas at Austin. He received his B.Eng., M.S.E., and Ph.D. in Electrical Engineering from McGill University.

@@

>>>>

\author[a]{Colin T. Sullender}
\author[a]{Adam Santorelli}
\author[a]{Lisa M. Richards}
\author[a]{Pawan K. Mannava}
\author[a]{Christopher Smith}
\author[a,*]{Andrew K. Dunn}
\affil[a]{Department of Biomedical Engineering, The University of Texas at Austin, Austin, TX, 78712, USA}

@@

\subsection*{Author Contributions}
C.T.S., L.M.R., and P.K.M. constructed the imaging system, conceived the experiments, and acquired the data. C.T.S., A.S., L.M.R., P.K.M., and C.S. analyzed the results. C.T.S, A.S., and L.M.R. wrote the manuscript. A.K.D. supervised the project. All authors contributed to manuscript revisions.

@@

\vspace{2ex}\noindent\textbf{Adam Santorelli} is a research associate at the University of Texas at Austin. He received his B.Eng., M.S.E., and Ph.D. in Electrical Engineering from McGill University. He was an IRC Government of Ireland Postdoctoral Fellow in the Translational Medical Device Lab at the National University of Ireland, Galway from 2017 to 2019. His current research is focused on the translational aspects of speckle imaging.

@@

\vspace{2ex}\noindent\textbf{Pawan K. Mannava} was an undergraduate researcher at the University of Texas at Austin when this research was conducted. He received his B.S. in Biomedical Engineering from the University of Texas at Austin.

\vspace{2ex}\noindent\textbf{Christopher Smith} is a graduate student at the University of Texas at Austin. He received his B.S. in Biomedical Engineering from the University of Houston.
